% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2007-2014 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
%
% This work is licensed under the Creative Commons Attribution-ShareAlike 3.0 Unported License. To view a copy of this license, visit http://creativecommons.org/licenses/by-sa/3.0/ or send a letter to Creative Commons, 171 Second Street, Suite 300, San Francisco, California, 94105, USA.

\documentclass[letterpaper,10pt]{article}

%-----------------------------------------------------------
\usepackage[empty]{fullpage}
\usepackage{color}
\usepackage{tabto}
\definecolor{mygrey}{gray}{0.80}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins to 0.5in on all sides
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.0in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{7.0in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------


\begin{document}

\begin{center}
\textbf{\huge Robert Olsthoorn}{\Large .com}
\end{center}
\begin{tabular*}{7in}{l@{\extracolsep{3.3in}}l}
+1-561-866-4321 &
\hfill\ rolsthoorn12@gmail.com \\
https://linkedin.com/in/rolstenhouse\ & \hfill\ https://github.com/rolstenhouse
\end{tabular*}
\\

\vspace{0.1in}

\resheading{Education}
\begin{itemize}
\item
	\ressubheading{University of Florida, Honors Program}{Gainesville, FL}{Bachelor of Science in Computer Engineering, Minor in Physics}{Aug. 2014 - May 2018}
	\begin{itemize}
		\resitem{GPA: 3.64/4.0}
	\end{itemize}

\item
	\ressubheading{Hong Kong University of Science and Technology}{Clearwater Bay, Hong Kong}{School of Engineering}{Feb. 2016 - May 2016}
\end{itemize}

\resheading{Work Experience}
\begin{itemize}
\item
	\ressubheading{Microsoft}{Redmond, WA}{Windows Core Team | Software Engineering Intern}{Sep. 2017 - Nov. 2017}
	\begin{itemize}
		\resitem{Developing kernel driver to support new DMA chipset}
	\end{itemize}
\item
	\ressubheading{Nextdoor | KPCB Engineering Fellow}{San Francisco, CA}{Monetization Team | Software Engineering Intern}{May 2017 - Aug. 2017}
	\begin{itemize}
		\resitem{Selected as 1 of 52 Engineering Fellows out of 2500 applicants}
		\resitem{Developed Ad inventory forecasting tool for advertising operations team}
		\resitem{Built python APIs to route SQS messages through an ad inventory management pipeline}
		\resitem{Wrote ad targeting evaluation test suite and redis cache update task}
	\end{itemize}
\item
	\ressubheading{Microsoft}{Redmond, WA}{Compiler and Language Platform Team | Explorer Intern}{May 2016 - Aug. 2016}
	\begin{itemize}
		\resitem{Created VS Code extension to support static analysis tool file format SARIF usisng TypeScript.}
	  \resitem{Authored PowerShell script to rewrite URIs referencing commit-dependent source files hosted in GitHub.}
		\resitem{Configured continuous integration platform, Appveyor, for static analysis tools supporting the SARIF standard.}
		\resitem{Refactored aspects of the SARIF SDK to comply with quality standards.}
	\end{itemize}
% \item
% 	\ressubheading{Infinite Energy}{Gainesville, FL}{Software Developer Intern}{Mar. 2015 - Aug. 2015}
% 	\begin{itemize}
% 		\resitem{Decreased page-load time for internal facing tool using AngularJS, C\#, \& .NET.}
% 		\resitem{Built user notification page for documents and alerts using AngularJS.}
% 		\resitem{Removed redundant argument from active-directory service function call.}
% 	\end{itemize}
% \item
% 	\ressubheading{Urban Darling, LLC}{Boca Raton, FL}{Web Developer Intern}{Jun. 2014 - May 2015}
% 	\begin{itemize}
% 		\resitem{Developed and maintained WordPress based website for wardrobe stylists.}
% 		\resitem{Managed design changes and modified template functionality using \textbf{PHP}.}
% 		\resitem{Improved Google PageSpeed score by decreasing page-load time through lossless image compression plugin.}
% 	\end{itemize}
\end{itemize}

\resheading{Projects}
\begin{itemize}
\item
	\ressubheading{PerfectPosture}{Tai Tam, Hong Kong}{Bitwise hacks: Awarded best software hack}{Feb. 2016}
	\begin{itemize}
		\resitem{Led development of OS X application to automatically dim laptop screen based on back-posture.}
		\resitem{Provided back-posture data through accelerometer on TI Launchpad implemented as a wearable.}
	\end{itemize}
\item
	\ressubheading{CheapSleep}{Atlanta, GA}{Hackstart: Awarded prize for Most Unique \& Problem-Solving App}{Jul. 2015}
	\begin{itemize}
		\resitem{Created an alarm clock which donated to a chosen charity per snooze.}
		\resitem{Implemented on the Android platform using the (deprecated) Venmo API.}
	\end{itemize}
\item
	\ressubheading{Bartertown, LLC}{Gainesville, FL}{CTO \& CoFounder}{May 2015 - Aug. 2015}
	\begin{itemize}
		\resitem{Accepted into HackerHouse startup incubator program}
		\resitem{Founded a social trading platform for the exchange of goods and services.}
		\resitem{Developed prototype using MeteorJS, Materialize and ElasticSearch}
		\resitem{Built real-time chat system, dynamic profile pages, push-to-git for deployment}
	\end{itemize}
% \item
% 	\ressubheading{Engineers Week}{Gainesville, FL}{UF College of Engineering Week of Events Software}{Nov. 2014 - Feb. 2015}
% 	\begin{itemize}
% 		\resitem{Led mobile site development using \textbf{jQuery} mobile and wrote custom event check-in.}
% 	\end{itemize}

\end{itemize}

% \resheading{Involvement}
% \begin{itemize}
% \item
%     \ressubheading{hackUST}{Feb. 2016 to Apr. 2016}{}{}
%     \begin{itemize}
%         \resitem{Member of organizing team for HKUST's hackathon}
%     \end{itemize}
% \item
%     \ressubheading{UF Programming Team}{Jan. 2015 to Dec. 2015}{}{}
%     \begin{itemize}
%         \resitem{Competed in Microsoft Coding Competition, UltiCoder, and Bloomberg's Codecon}
%     \end{itemize}
% \item
%     \ressubheading{UF Association For Computing Machinery}{Jan. 2015 to Dec. 2015 }{}{}
%     \begin{itemize}
%         \resitem{Managed corporate sponsorships and organization's finances.}
%     \end{itemize}
% \end{itemize}

\resheading{Involvement}
\newline \newline
- (2017) Salsero in the Gator Salsa Club\newline
- (2016) TA (Teaching Assistant) for CodePath Internship Preparation \newline
- (2016) Assisted in organizing \textbf{hackUST}, Hong Kong's largest student-led hackathon. \newline
- (2015) Competed in CodeJam, Bloomberg's Codecon, Ulticoder, etc as a member of the \textbf{UF Programming Team}. \newline
- (2015) Held Treasurer executive board position of the \textbf{UF ACM chapter}.\newline

\resheading{Skills}
\newline\newline
\textbf{Languages:} \tabto{2.5cm} Python, C, asm, Java, Javascript, C{}\verb!++!, SQL \newline
% \textbf{Frameworks:} \tabto{2.5cm} MeteorJS, Materialize, AngularJS, WordPress, Semantic UI, jekyll

\end{document}
